\section{Web Service Solutions}
An attractive feature for a web application could be to providing services that other applications can use to interact it. To provide this functionality different methods such as: shared database, remote producer call, message bus and file transfer been developed.

Shared database can work for multiple applications within the same organization but on a larger scale involving multiple organization it an very insecure solution and even more complex to pull off.

File transfer is only available within the same application were it can access the data on the harddrive. This principle was generalized so it was possible to communicate between multiple computers through remote procedure calls. Remote procedure calls can work by using synchronous communication where an application sends a request and waits for the answer. This poses some downtime while it waits for the answer. Another way is to use asynchronous communication were a queues are implemented to act as a intermediate step for storing the requests and responses.
The remote procedure call abstraction covers how the operating system works and communicates with the communication protocols, how the data is transferred and verification of the delivery.

REST is a series of principles which helps web services to communicate through procedure calls. It utilizes a uniform interface which the applications can communicate through. All transfer goes through the hyperlinks and data are represented in lightweight formats as plain text or JSON. REST works by sending a request through HTTP and the server then processes this request and returns the result as HTTP result eg. an JSON. REST is easily set up does not require a lot of time to set up. A limit of REST is that using all 4 verbs. which allows for database manipulation. Another disadvantage is that REST sends all content for HTTP or HTTPS which means is it possible to preform a man in the middle attack and listen to the transactions.

SOAP is a protocol while REST on the other hand is an architecture. SOAP takes more effort compared to REST to setup but provide more security and a bigger flexibility in terms of requesting data and the format in which you receive. SOAP general is setup by creating an envelopes which describes how to request for messages and how to process them. This message is then process on server site through a transaction manager which insures that the transaction is completed correctly. The disadvantage of SOAP is that it is were complex and requires work to setup probably.